---
title: "Injuries"
---

Soccer injuries may vary depending on the position. The following data was used with the tidyverse, plotly, and ggplot2 packages. Then, I selected the important data columns to analyze the relationship between position and injuries in the **Premier League**. This was then used to visualize positions compared to injuries in an inuitive format that clearly shows the relationship. I did this by putting the positions from the beginning to end of field, and the injuries from toes to heads on the body.

Note that in both of the following plots:

**Other** injuries are illness or tiredness (Plot 1)

**Other_body** is anywhere on the body where the player feels ill or tired (Plot 2)

Also, these plots are interactive so if the reader hovers above each of the points, they can see the players injury, position, and club.

```{r}
#| echo: false
#| output: false
library(tidyverse)
library(readxl)
library(plotly)
library(ggiraph)
library(gganimate)
library(dplyr)

prem_league_stats <- read_excel("../Final-project/prem_league_stats.xlsx")
```
### Injury Plot 1 (Specific)

This plot shows all the types of injuries compared to position, with position at the x axis, and injuries at the y axis. Then, I color coded the dots to represent the current club that the player is on.

Note: "Other" injuries are illness or tiredness



```{r}
#| echo: false
#| message: false
#| warning: false
prem_league_plot_int <- prem_league_stats|>
select(part_of_body, injury, position, `Current Club`, age, full_name)|>
drop_na(part_of_body, injury)|>
ggplot(mapping = aes(x = position,
                     y = injury,
                     text = paste("Name:",full_name, "\n",
                                  "Team:", `Current Club`, "\n",
                                  "Pos:", position, "\n",
                                  "Injury:", injury, "\n"),
                     color = `Current Club`)) +
geom_jitter(size = 1.5)+
labs(title = "Different Soccer Injuries Related to Position",
     x = "Positions",
     y = "Type of Injury")
ggplotly(prem_league_plot_int, tooltip = "text")
```

From this, we can takeaway that:

There are more **thigh** injuries in defending

There are more **knee** injuries in the forward position

There are more **thigh** injuries in goalkeeping

There are more **thigh** injuries in the midfielding position

### Injury Plot 2 (Broad)


This is a more broad scatterplot of the one above. Instead of each injury being listed, I have grouped them by the region of body where the injury has happened.

Note: "Other_body" is anywhere on the body where the player feels ill or tired


```{r}
#| echo: false
#| message: false
#| warning: false
prem_league_plot_int <- prem_league_stats|>
select(part_of_body, injury, position, `Current Club`, age, full_name)|>
drop_na(part_of_body, injury)|>
ggplot(mapping = aes(x = position,
                     y = part_of_body,
                     text = paste("Name:",full_name, "\n",
                                  "Team:", `Current Club`, "\n",
                                  "Pos:", position, "\n",
                                  "Injury:", injury, "\n"),
                     color = `Current Club`)) +
geom_jitter(size = 1.5)+
labs(title = "Different Soccer Injuries Related to Position",
     x = "Positions",
     y = "Type of Injury")
ggplotly(prem_league_plot_int, tooltip = "text")
```

From this, we can takeaway that there are more lower body injuries for all of the positions