---
title: "Home"
editor: visual
---

The **Premier League** is located in England and is one of the most competetive leagues out of all the soccer leagues. There are 20 teams in the Premier League, and I analyzed the positions and ages of all the players in the Premier League who suffered from an injury in the 2022/2023 season. Using data from Footystats, I found out that the positions that generate the most injuries are Defenders and Midfielders mainly in the lower body. Also, most injuries happen between the ages of 20 and 30


### This is one of my main plots that you can find on the injuries page with further explanation



```{r}
#| echo: false
#| output: false
library(tidyverse)
library(readxl)
library(plotly)
library(ggiraph)
library(gganimate)
library(dplyr)

prem_league_stats <- read_excel("../Final-project/prem_league_stats.xlsx")
```


```{r}
#| echo: false
#| message: false
#| warning: false
prem_league_plot_int <- prem_league_stats|>
select(part_of_body, injury, position, `Current Club`, age, full_name)|>
drop_na(part_of_body, injury)|>
ggplot(mapping = aes(x = position,
                     y = injury,
                     text = paste("Name:",full_name, "\n",
                                  "Team:", `Current Club`, "\n",
                                  "Pos:", position, "\n",
                                  "Injury:", injury, "\n"),
                     color = `Current Club`)) +
geom_jitter(size = 1.5)+
labs(title = "Different Soccer Injuries Related to Position",
     x = "Positions",
     y = "Type of Injury")
ggplotly(prem_league_plot_int, tooltip = "text")
```
